risk-perception

### 2019-10-11 risk-percption.Rmd
crop yields

@@

What about memory of risk?
```{r}
test <- runif(7) < .5

remember <- function(x, y) {
  x +  * .1 - .01 * x
}

1

(1-1 )/1

remember
accumulate(test, ~remember(.x, .y)) %>% plot

@@

test2 <- runif(50) < .2

a <- Y + (n*m) -1
b <- N - Y + (n*(1-m)) - 1
a = n * m
b = n * (1 - m)

.5 * 3

learn <- function(x, event) {
  x %>%
    mutate(alpha = event + alpha,
           beta = beta + 1 - event,
           mu = alpha / (alpha + beta),
           estimate = map2_dbl(alpha, beta, ~rbeta(1, .x, .y)))
}
learn(test, TRUE)

accumulate(test2, ~learn(.x, .y), .init = test) %>% bind_rows %>% pull(estimate) %>% plot
```

@@

calc_wheat_yield <- function(rainfall) {
  yield_max_wheat * kcal_wheat * pmax(0, 0.51 * log(rainfall) + 1.03)  # annual rainfall impact on yields
}

calc_barley_yield <- function(rainfall) {
  yield_max_barley * kcal_barley * pmax(0, 0.48 * log(rainfall) + 1.51)  # annual rainfall impact on yields
}

tibble(rainfall = (0:200) / 100,
       barley = calc_barley_yield(rainfall),
       wheat = calc_wheat_yield(rainfall)) %>%
  gather(crop, yield, barley:wheat) %>%
  ggplot(aes(rainfall, yield, color = crop)) + geom_line()

>>>>

test2 <- c((runif(25) < .2),(runif(25) < .5), runif(25) < .1)
tibble(time = 1:75,
       drought = test2) %>%
  mutate(period = round(time, -1)) %>%
  add_count(period) %>%
  filter(period >= 10) %>%
  group_by(period) %>%
  summarise(drought = sum(drought)) %>%
  ggplot(aes(period, drought)) +
  geom_col()
```

```{r}
learn <- function(agents, event) {
  agents %>%
    mutate(alpha = event + alpha,
           beta = beta + 1 - event,
           mu = alpha / (alpha + beta),
           estimate = map2_dbl(alpha, beta, ~rbeta(1, .x, .y)))
}

accumulate(test2, ~learn(.x, .y), .init = test) %>% bind_rows(.id = 'time') %>% qplot(as.numeric(time), estimate, data = ., geom = 'point')
```

```{r}
learn(test, TRUE)
```

@@

@@

@@

calc_yield <- function(rainfall, crop = 'wheat') {
  if (crop == 'wheat') {
    yield <- yield_max_wheat * kcal_wheat * pmax(0, 0.51 * log(rainfall) + 1.03)  # annual rainfall impact on yields
  }

  if(crop == 'barley') {
    yield <- yield_max_barley * kcal_barley * pmax(0, 0.48 * log(rainfall) + 1.51) 
  }

  return(yield)
}

tibble(rainfall = (0:200) / 100,
       barley = calc_yield(rainfall, 'barley'),
       wheat = calc_yield(rainfall, 'wheat')) %>%
  gather(crop, yield, barley:wheat) %>%
  ggplot(aes(rainfall, yield, color = crop)) + 
  geom_line() +
  geom_hline(yintercept = yield_max_wheat * kcal_wheat) +
  geom_hline(yintercept = yield_max_barley * kcal_barley)
```
